\documentclass{article}

\usepackage[pdftex]{graphicx}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\setlength{\parindent}{0pt}
\pdfpagewidth 8.5in
\pdfpageheight 11in

\begin{document}



\begin{titlepage}

\begin{center}


% Upper part of the page
   

\textsc{\LARGE University of Limerick}\\[1.5cm]

\textsc{\Large Final year project}\\[0.5cm]

\textsc{\Large Interim Report}\\[0.5cm]

% Title
\HRule \\[0.4cm]
{ \huge \bfseries Litter Tracking Smartphone Appliction}\\[0.4cm]

\HRule \\[1.5cm]

% Author and supervisor
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
John \textsc{Patrick Russell - 0734004}
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
Mr.~Micheal \textsc{Coughlan}
\end{flushright}
\end{minipage}

\vfill

% Bottom of the page
{\large \today}

\end{center}

\end{titlepage}
\newpage
\tableofcontents
\newpage

\label{sec:Summary}
\section{Project Summary}
This project is an application for a smart phone targeted at keeping the banks of the river Shannon and other areas clean of litter. This application will work by a user locating a piece of litter, taking a picture of it. The location of the user when the picture is taken will corrospond to the location of this particular piece of litter. This data must be stored in a remote location.

\paragraph{}
\label{par:First Paragraph}

Smartphone's have become much more widespread and popular amoungst modern society. This can be attributed to the progress technology has made in making very powerful devices which fit in our pocket. Smartphone use is constantly on the up at the moment so this is a market which is still growing.

\paragraph{}
\label{par:Second Paragraph}

To incorporate all the functionality mentioned above the application must conform to the points mentioned.
The ability to obtian images from the devices camera will be necessary to capture the photo.
For this applicaition to work the GPS coordinates or location coordinates must be obtained when a photo is taken
The data obtained (photo and location) must be stored in a remote server for users to view and to store.

\paragraph{}
\label{par:Third Paragraph}
To work with all of the above mentioned functionality a suitable device must be picked.



\newpage


\label{sec:Subsection}
\section{Introduction}
\subsection{General Information}
\subsection{Motivation Factors}
\subsection{Objectives of Proposed Work}
\subsection{Structure of Report}
\newpage

\label{sec:Motivation}
\section{Research}
\subsection{Geo Caching}
\subsection{Platforms}
\subsection{Software and Language}
\subsection{Web Services}
\newpage


\label{sec:Objectives}
\section{Description of Current Progress}
\newpage

\label{sec:Objectives}
\section{Project Plan}



\end{document}
